---
title: "Innovation_Diversity"
author: "Steven Nichols"
date: "November 27, 2016"
output:
  html_document: 
    highlight: monochrome
    keep_md: yes
    number_sections: yes
    theme: journal
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##read in DFs and combine diversity and innovation measures 

```{r}

library(MASS)
library(psych)
setwd("C:\\Users\\Steven\\Google Drive\\1. MOT\\1) Fall 2016\\2. Global Innovation\\Assignments\\Final Paper\\Data")

diversity <- read.csv("diversity.csv")
rinnovation <- read.csv("innovation.csv")
head(diversity)
head(innovation)

innovation <- subset(innovation, select=c("Country.Economy", "Score..0.100.", "Rank", "Income", "Rank.1", "Region" ))
innovation['Country'] <- innovation$Country.Economy
master <- merge(diversity, innovation, by="Country")

```

##create separate subset for analysis of correlations

```{r} 
names(master)
master['Score_Innovation'] <- master$Score..0.100.
master['Score_Diversity'] <- master$weighted.index
master['Gender'] <- master$gender

master$weighted.index <- NULL
master$Score..0.100. <-NULL
master['Income'] <- master$income
head(master)
diversity_breakdown <- subset(master, select=c("Gender", "Language", "Country.of.birth", "Age", "Part.time", "Education", "Income", "Sector", "Score_Innovation", "Score_Diversity"))
head(master)
d <- cor(diversity_breakdown)
d
```

#create visual correlation matrix to study intersection of diversity and innovation 

```{r, echo=FALSE}
library(corrplot)
corrplot(d, method="pie")

```

```{r}

head(innovation)
norway <- subset(innovation, Country == "Norway")
norway
norway_diversity <- subset(diversity, Country == "Norway")
norway_diversity 
innovation
```

##Analyze power distance as a predictor of innovation and diversity 

```{r} 

pd <- read.csv("pdi.csv")
pd
head(pd)
div_innovation <- subset(master, select=c("Country", "Gender", "Language", "Country.of.birth", "Age", "Part.time", "Education", "Income", "Sector", "Score_Innovation", "Score_Diversity"))
pd_innovation <- merge(pd, div_innovation, by="Country")
head(pd_innovation)
pd_cor <- pd_innovation
pd_cor$Country <- NULL

p <- cor(pd_cor)
p
corrplot(p, method="pie")

AsianEconomies <- c("China", "Japan", "South Korea")
WesternEconomies <- c("United States", "United Kingdom", "Germany")

pd_innovation_Asia <- pd[pd$Country %in% AsianEconomies,]
pd_innovation_West <- pd[pd$Country %in% WesternEconomies,]

PDI_Asia_Avg <- (sum(pd_innovation_Asia$PDI))/nrow(pd_innovation_Asia)
PDI_West_Avg <- (sum(pd_innovation_West$PDI))/nrow(pd_innovation_West)
Asia_Avg
West_Avg
pd$PDI
max(pd$PDI)
min(pd$PDI)
